### 2017-02-07 doc/manuscript.Rmd
Created and added GEE with PLS scores code and results

cor_df <- analyze_corr()
cor_df_mol <- analyze_corr(y = tg_pct)
cor_df_tagfa <- analyze_corr_tagfa()
```

@@

The beta-cell function PLS results showed clustering of similar fatty acids,
however there there was a low correlation (though significant at 
p`r cor_pls_igi$p`) between the predicted values and the actual values 
(r=`r cor_pls_igi$r` to `r cor_pls_issi2$r`), suggesting poor predictability.
Given the low predictability, only the insulin sensitivity measures are
presented.

>>>>

cor_df <- analyze_corr()
cor_df_mol <- analyze_corr(y = tg_pct)
cor_df_tagfa <- analyze_corr_tagfa()

pls_gee <- project_data %>%
    analyze_gee(
        x = c('Comp1', 'Comp2'),
        data_prep = 'pls',
        pls_results = pls_isi
        ) %>% 
    dplyr::select(Yterms, Xterms, estimate, p.value) %>% 
    dplyr::filter(Xterms == 'Comp1') %>% 
    dplyr::mutate(p.value = format_p(p.value),
                  estimate = format_rounding(estimate))
```

@@

The beta-cell function PLS results showed clustering of similar fatty acids,
however there there was a low correlation (though significant at 
p`r cor_pls_igi$p`) between the predicted values and the actual values 
(r=`r cor_pls_igi$r` to `r cor_pls_issi2$r`), suggesting poor predictability.
Given the low predictability, only the insulin sensitivity measures are
presented. We used the extracted PLS scores as the predictor variable in the GEE
models and found negative associations of the first component on all outcome
variables, with the strongest association being with the insulin sensitivity
variables (beta=`r pls_gee$estimate[3]`, all p`r pls_gee$p.value[1]`; using PLS
scores constrained by ISI).
